PANCHANGE_variable_creation

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
added figure knit to descriptive rmds. Fixed exclusions for MH diagnosis

@@

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "four_cohorts_variables.rds"))
dim(dat.raw)
colnames(dat.raw)
```

@@

```{r Exclusion criteria for PANCHANGE}
dat <- dat.raw %>%
  filter( # Participants should have responded to the mental health diagnosis (MHD) questionnaire
  !is.na(depressive_disorders) &
 !is.na(anxiety_disorders) &
  !is.na(eating_disorders) &
  !is.na(obsessive_compulsive_disorders) &
 !is.na(psychotic_disorders) &
  !is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  !is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  !is.na(autism_spectrum_disorder) &
  !is.na(mhd.attention_deficit_hyperactivity_disorder) &
  !is.na(mhd.personality_disorder) &
  !is.na(control)
  ) %>% 
 filter(
   !is.na(data_group_gad) & # Participants should have answered at least the GAD, the PHQ, or the PCL once
   !is.na(data_group_phq) &
   !is.na(data_group_pcl)
 ) %>%
  drop_na(startDate.coping) %>% # Participant has answered the COPING/RAMP baseline questionnaire
  drop_na(Gender_collapsed) %>% # Participant has self-reported their gender
  drop_na(age_category_collapsed) # Participant has self-reported their age

@@

>>>>

knitr::opts_chunk$set(fig.path="figures/")

@@

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "four_cohorts_variables.rds"))
dim(dat.raw)

@@

```{r Exclusion criteria for PANCHANGE}
dat <- dat.raw %>%
  filter( # Participants should have responded to the mental health diagnosis (MHD) questionnaire
  (!is.na(depressive_disorders) &
 !is.na(anxiety_disorders) &
  !is.na(eating_disorders) &
  !is.na(obsessive_compulsive_disorders) &
 !is.na(psychotic_disorders) &
  !is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  !is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  !is.na(autism_spectrum_disorder) &
  !is.na(mhd.attention_deficit_hyperactivity_disorder) &
  !is.na(mhd.personality_disorder) &
  !is.na(control)) |
  !is.na(DidNotRespondMHD)
  ) %>% 
 filter(
   !is.na(data_group_gad) & # Participants should have answered at least the GAD, the PHQ, or the PCL once
   !is.na(data_group_phq) &
   !is.na(data_group_pcl)
 ) %>%
  drop_na(startDate.coping) %>% # Participant has answered the COPING/RAMP baseline questionnaire
  drop_na(Gender_collapsed) %>% # Participant has self-reported their gender
  drop_na(age_category_collapsed) # Participant has self-reported their age

@@

# frequencies and descriptives in exclusion data

### 2020-12-16 PANCHANGE_variable_creation.Rmd
added figure knit to descriptive rmds. Fixed exclusions for MH diagnosis

```{r Collapse Ethnicity}
dat <- dat %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0, #European
             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
             Ethnicity_numeric == 4 ~ 3, #African or African British
             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
           )
  )

@@

dat %>%
  freq(prepandemic_9_months)
```

>>>>

```{r Collapse Ethnicity}
dat <- dat %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0, #European
             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
             Ethnicity_numeric == 4 ~ 3, #African or African British
             Ethnicity_numeric == 5 ~ 4, #Arab - combined with African/African British
             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
           )
  )

@@

dat %>%
  freq(prepandemic_9_months)
```
## create a variable for chose not to respond to the Mental health questions

```{r choce not to respond MHD}

dat <- dat %>%
  mutate(DidNotRespondMHD  = 
           case_when(
             (is.na(depressive_disorders) &
 is.na(anxiety_disorders) &
  is.na(eating_disorders) &
  is.na(obsessive_compulsive_disorders) &
 is.na(psychotic_disorders) &
  is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
  is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
  is.na(autism_spectrum_disorder) &
  is.na(mhd.attention_deficit_hyperactivity_disorder) &
  is.na(mhd.personality_disorder) &
  is.na(control)) ~ 1))

```
